### 2018-09-07 monograph/thesis/chapters/object_beautifier.tex
Added draft notes to object_beautifier.tex

@@

This work aims to create a formatter (single software) of easy configuration
and expansion capable of encompassing the programming languages that exist,
based on a specific use of regular expressions. The strategy is not to be
relaying on the syntax of the programming languages parsed. With it in mind,
we will treat them as a common text, and it will be up to the end user to
configure the transformations/formatting to be applied in the text, giving
reasonably more freedom to easily configure several programming languages
(if not them all), taking advantage of the fact which many of them share
similar structures if not identical.

>>>>

Criar uma nova linguagem para entrar com a syntaxe como sublime text, mas sem utilizar YAML.
Assim, faz isso como trabalho final de compiladores, onde o seu backend será o formatador.

~Use lark to enter the language grammars, instead writing a syntax parser like Sublime Text YAML .sublime-syntax files.~
\begin{lstlisting}
_parser = lark.Lark(r"""
    productions   : empty_line* ( non_terminal_start "->" non_terminals end_symbol )* non_terminal_start "->" non_terminals end_symbol?
    non_terminals : production ( "|" production )*
    production    : epsilon | terminal non_terminal?

    // Forces them to appear in the tree as branches
    epsilon      : [] | "&"
    end_symbol   : ";" NEWLINE+ | NEWLINE+
    terminal     : SIGNED_NUMBER | LCASE_LETTER
    non_terminal : UCASE_LETTER+ ( DIGIT | "'" )*
    empty_line   : NEWLINE

    // Rename the start symbol, so when parsing the tree it is simple to find it
    non_terminal_start : non_terminal

    // Tells the tree-builder to inline this branch if it has only one member
    ?non_terminal_epsilon : non_terminal | epsilon

    // Stops Lark from automatically filtering out these literals from the tree
    null   : "null"
    true   : "true"
    false  : "false"

    // Import common definitions
    %import common.INT
    %import common.DIGIT
    %import common.UCASE_LETTER
    %import common.LCASE_LETTER
    %import common.SIGNED_NUMBER
    %import common.NEWLINE
    %import common.WS_INLINE

    // Set to ignore white spaces
    %ignore WS_INLINE
""", start='productions' )
\end{lstlisting}

@@

TODO:
Explains what does `translation` means and what is a translator,
compiler,
etc.
(the first slide contents' from Introdução a Compiladores)

This work aims to propose a translator,
where the input and output languages are the same language.
Such translation objective is to change the language representational structure,
but without affecting the language lex,
syntactic or semantics, i.e.,
the language meaning.

This program class is commonly know as text formatters.
The differential from this work from others is the goal of a single expandable tool,
capable of manipulating all existent and future programming languages,
based on the use of deterministic \cite{TODO:
deterministic free grammars explanation} and controlled nondeterministic \cite{TODO:
section explaning what does controlled means} context free grammars.

This audacious goal,
can only be accomplished because the proposed tool does not rely on the lex,
syntax and semantic aspects \cite{TODO:
what does these languages aspects are} of any used languages.
Therefore,
it is up to this tool users\s to write the lex and syntactic,
but they are not required to write the semantic aspects of the desired language,
as the objective of text formatters is to change the structural aspects \cite{TODO:
what are the source code formatters objectives}.

.sublime-syntax or my .object-beauty is a meta-language, as EBNF \cite{Extended Backus–Naur form}.

With this approach, it is not required for the user to input language\s grammar is

 After tool\s user aspects specification, we will treat them as a common text,
and it will be up to the end user to configure the transformations/formatting to be applied in the text,
giving reasonably more freedom to easily configure several programming languages (if not them all),
taking advantage of the fact which many of them share similar structures if not identical.
